\documentclass{article}\usepackage{amsmath}\begin{document}\title{Simplex Solver}\maketitle\begin{flushleft}\textbf{Problem}\end{flushleft}\begin{flushleft}Given the following linear system and objective function, find the optimal solution.\end{flushleft}\begin{equation*}\max{ 3x_1 + 2x_2 } \\ \end{equation*}\[\left\{\begin{array}{c} x_1 + 2x_2 \leq 5 \\  3x_1 - x_2 \leq 4 \\ \end{array}\right.\]\begin{flushleft}\textbf{Solution}\end{flushleft}\begin{flushleft}Add slack variables to turn all inequalities to equalities.\end{flushleft}\[\left\{\begin{array}{c} x_1 + 2x_2 + s_1 = 5 \\  3x_1 - x_2 + s_2 = 4 \\ \end{array}\right.\]\begin{flushleft}Create the initial tableau of the new linear system.\end{flushleft}\begin{equation*}\begin{bmatrix}\begin{array}{cccc|c}x_1 &x_2 &s_1 &s_2 &b \\ \hline1 & 2 & 1 & 0 & 5 \\3 & -1 & 0 & 1 & 4 \\ \hline-3 & -2 & 0 & 0 & 0 \\\end{array}\end{bmatrix}\begin{array}{c}\\s_1 \\s_2 \\\\\end{array}\end{equation*}\begin{flushleft}There are negative elements in the bottom row, so the current solution is not optimal. Thus, pivot to improve the current solution. The entering variable is $x_1$ and the departing variable is $s_2$.\end{flushleft}\begin{flushleft}Perform elementary row operations until the pivot element is 1 and all other elements in the entering column are 0.\end{flushleft}\begin{equation*}\begin{bmatrix}\begin{array}{cccc|c}x_1 &x_2 &s_1 &s_2 &b \\ \hline0 & 7/3 & 1 & -1/3 & 11/3 \\1 & -1/3 & 0 & 1/3 & 4/3 \\ \hline0 & -3 & 0 & 1 & 4 \\\end{array}\end{bmatrix}\begin{array}{c}\\s_1 \\x_1 \\\\\end{array}\end{equation*}\begin{flushleft}There are negative elements in the bottom row, so the current solution is not optimal. Thus, pivot to improve the current solution. The entering variable is $x_2$ and the departing variable is $s_1$.\end{flushleft}\begin{flushleft}Perform elementary row operations until the pivot element is 1 and all other elements in the entering column are 0.\end{flushleft}\begin{equation*}\begin{bmatrix}\begin{array}{cccc|c}x_1 &x_2 &s_1 &s_2 &b \\ \hline0 & 1 & 3/7 & -1/7 & 11/7 \\1 & 0 & 1/7 & 2/7 & 13/7 \\ \hline0 & 0 & 9/7 & 4/7 & 61/7 \\\end{array}\end{bmatrix}\begin{array}{c}\\x_2 \\x_1 \\\\\end{array}\end{equation*}\begin{flushleft}There are no negative elements in the bottom row, so we know the solution is optimal. Thus, the solution is: \end{flushleft}\begin{equation*}s_1 = 0, s_2 = 0, x_1 = \frac{13}{7}, x_2 = \frac{11}{7}, z = \frac{61}{7}\end{equation*}\end{document}